ABM simulating short-term mating behaviors

### 2022-06-02 submission/manuscript.tex
added confidence interval in the results section, close #21

The results from Experiment 1 showed that when there were gender
differences in preferences for short-term mating, there was no gender
difference in the average number of short-term mating experiences among
the full population of heterosexual individuals
(\emph{M\textsubscript{men}} = 1.43, \emph{SD\textsubscript{men}} =
0.24; \emph{M\textsubscript{women}} = 1.43,
\emph{SD\textsubscript{women}} = 0.24), Cohen's \emph{d} = 0.00. Nor was
there a difference in the average number of short-term mates
(\emph{M\textsubscript{men}} = 0.80, \emph{SD\textsubscript{men}} =
0.11; \emph{M\textsubscript{women}} = 0.80,
\emph{SD\textsubscript{women}} = 0.11), Cohen's \emph{d} = 0.00 (Figure
\ref{fig:men_vs_women}).

@@

The results from Experiment 2 showed that when there were gender
differences in preferences for short-term mating, there were gender
differences in short-term mating behaviors between gay men and lesbian
women (Figure \ref{fig:men_vs_women}). The average number of short-term
mating experiences was higher among gay men (\emph{M} = 2.63, \emph{SD}
= 0.37) than among lesbian women (\emph{M} = 0.32, \emph{SD} = 0.10),
\emph{t}(4,998) = -301.78, \emph{p} \textless{} .001, Cohen's \emph{d} =
8.54. Similarly, the average number of short-term mates was higher among
gay men (\emph{M} = 1.72, \emph{SD} = 0.19) than among lesbian women
(\emph{M} = 0.25, \emph{SD} = 0.07), \emph{t}(4,998) = -357.69, \emph{p}
\textless{} .001, Cohen's \emph{d} = 10.12.

@@

In Experiment 1, there was a smaller proportion of heterosexual men in
the mating pool (\emph{M} = 0.38, \emph{SD} = 0.04) compared to women
(\emph{M} = 0.51, \emph{SD} = 0.05), \emph{t}(4,998) = 104.85, \emph{p}
\textless{} .001, Cohen's \emph{d} = 2.97. In this population, there
were gender differences in short-term mating behaviors when men and
women had differential preferences for short-term mating (Figure
\ref{fig:men_vs_women_inpool}). The average number of short-term mating
experiences was higher among heterosexual men (\emph{M} = 3.78,
\emph{SD} = 0.50) than among heterosexual women (\emph{M} = 2.79,
\emph{SD} = 0.35), \emph{t}(4,998) = -81.53, \emph{p} \textless{} .001,
Cohen's \emph{d} = 2.31. Likewise, the average number of short-term
mates was higher among heterosexual men (\emph{M} = 2.12, \emph{SD} =
0.17) than among heterosexual women (\emph{M} = 1.56, \emph{SD} = 0.11),
\emph{t}(4,998) = -135.85, \emph{p} \textless{} .001, Cohen's \emph{d} =
3.84.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/fig2_men_vs_women_inpool.pdf}
  \caption{\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables. Plot (A) shows the average number of short-term mating experiences in the mating pool, and plot (B) shows the average number of short-term mates in the mating pool. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. The averages were calculated using the population of heterosexual men and women in the mating pool (\textit{M\textsubscript{men}} = 56.85, \textit{M\textsubscript{men}} = 77.04).}
  \label{fig:men_vs_women_inpool}
\end{figure}

@@

Gay men engaged in short-term mating behaviors more than heterosexual
men did (Figure \ref{fig:hetero_vs_gay}). The average number of
short-term mating experiences (as calculated using the full population
of men) was higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37)
than among heterosexual men (\emph{M} = 1.43, \emph{SD} = 0.24),
\emph{t}(4,998) = -134.87, \emph{p} \textless{} .001, Cohen's \emph{d} =
3.81. Similarly, the average number of short-term mates (as calculated
using the full population of men) was higher among gay men (\emph{M} =
1.72, \emph{SD} = 0.19) than among heterosexual men (\emph{M} = 0.80,
\emph{SD} = 0.11), \emph{t}(4,998) = -206.91, \emph{p} \textless{} .001,
Cohen's \emph{d} = 5.85.

>>>>

The results from Experiment 1 showed that when there were gender
differences in preferences for short-term mating, there was no gender
difference in the average number of short-term mating experiences among
the full population of heterosexual individuals
(\emph{M\textsubscript{men}} = 1.43, \emph{SD\textsubscript{men}} =
0.24; \emph{M\textsubscript{women}} = 1.43,
\emph{SD\textsubscript{women}} = 0.24), Cohen's \emph{d} = 0.00, 95\% CI
= --0.01 to 0.01. Nor was there a difference in the average number of
short-term mates (\emph{M\textsubscript{men}} = 0.80,
\emph{SD\textsubscript{men}} = 0.11; \emph{M\textsubscript{women}} =
0.80, \emph{SD\textsubscript{women}} = 0.11), Cohen's \emph{d} = 0.00,
95\% CI = --0.01 to 0.01 (Figure \ref{fig:men_vs_women}).

@@

The results from Experiment 2 showed that when there were gender
differences in preferences for short-term mating, there were gender
differences in short-term mating behaviors between gay men and lesbian
women (Figure \ref{fig:men_vs_women}). The average number of short-term
mating experiences was higher among gay men (\emph{M} = 2.63, \emph{SD}
= 0.37) than among lesbian women (\emph{M} = 0.32, \emph{SD} = 0.10),
\emph{t}(4,998) = --301.78, \emph{p} \textless{} .001, Cohen's \emph{d}
= 8.54, 95\% CI = --2.33 to --2.30. Similarly, the average number of
short-term mates was higher among gay men (\emph{M} = 1.72, \emph{SD} =
0.19) than among lesbian women (\emph{M} = 0.25, \emph{SD} = 0.07),
\emph{t}(4,998) = --357.69, \emph{p} \textless{} .001, Cohen's \emph{d}
= 10.12, 95\% CI = --1.48 to --1.46.

@@

In Experiment 1, there was a smaller proportion of heterosexual men in
the mating pool (\emph{M} = 0.38, \emph{SD} = 0.04) compared to women
(\emph{M} = 0.51, \emph{SD} = 0.05), \emph{t}(4,998) = 104.85, \emph{p}
\textless{} .001, Cohen's \emph{d} = 2.97, 95\% CI = 0.13 to 0.14. In
this population, there were gender differences in short-term mating
behaviors when men and women had differential preferences for short-term
mating (Figure \ref{fig:men_vs_women_inpool}). The average number of
short-term mating experiences was higher among heterosexual men
(\emph{M} = 3.78, \emph{SD} = 0.50) than among heterosexual women
(\emph{M} = 2.79, \emph{SD} = 0.35), \emph{t}(4,998) = --81.53, \emph{p}
\textless{} .001, Cohen's \emph{d} = 2.31, 95\% CI = --1.02 to --0.97.
Likewise, the average number of short-term mates was higher among
heterosexual men (\emph{M} = 2.12, \emph{SD} = 0.17) than among
heterosexual women (\emph{M} = 1.56, \emph{SD} = 0.11), \emph{t}(4,998)
= --135.85, \emph{p} \textless{} .001, Cohen's \emph{d} = 3.84, 95\% CI
= --0.57 to --0.55.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/fig2_men_vs_women_inpool.pdf}
  \caption{\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables. Plot (A) shows the average number of short-term mating experiences in the mating pool, and plot (B) shows the average number of short-term mates in the mating pool. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. The averages were calculated using the population of heterosexual men and women in the mating pool (proportion: \textit{M\textsubscript{men}} = 0.38, \textit{M\textsubscript{women}} = 0.51).}
  \label{fig:men_vs_women_inpool}
\end{figure}

@@

Gay men engaged in short-term mating behaviors more than heterosexual
men did (Figure \ref{fig:hetero_vs_gay}). The average number of
short-term mating experiences (as calculated using the full population
of men) was higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37)
than among heterosexual men (\emph{M} = 1.43, \emph{SD} = 0.24),
\emph{t}(4,998) = --134.87, \emph{p} \textless{} .001, Cohen's \emph{d}
= 3.81, 95\% CI = --1.21 to --1.18. Similarly, the average number of
short-term mates (as calculated using the full population of men) was
higher among gay men (\emph{M} = 1.72, \emph{SD} = 0.19) than among
heterosexual men (\emph{M} = 0.80, \emph{SD} = 0.11), \emph{t}(4,998) =
--206.91, \emph{p} \textless{} .001, Cohen's \emph{d} = 5.85, 95\% CI =
--0.92 to --0.91.
